Automatic Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Handlebar Perturbations\\Version 2.dev

### 2024-09-20 main.tex
Noted which bicycleparameter rider was used.

\section*{Appendix}
%
Physical parameters and estimated uncertainty (standard deviation) for the
balance assist bicycle without and with the rider. These are derived from the
measurement approach in \citet{Moore2012}. Variable names match the notation
from the benchmark bicycle model presented in \citet{Meijaard2007}.

>>>>

\section*{Appendix}
%
Physical parameters and estimated uncertainty (standard deviation) for the
balance assist bicycle without and with the rider. These are derived from the
measurement approach in \citet{Moore2012}. The rider inertial parameters are
derived from the rider ``Jason'' available in BicycleParameters
1.1.1~\citep{Moore2024}. The variable names match the notation from the
benchmark bicycle model presented in \citet{Meijaard2007}.
